Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-09-14 Ben_Manuscripts/structure_paper/Draft.tex
Comments.

  Since the dynamics of this system appear to be quite slow, and consequently most of
  our analysis has been focused on a small set of quenched configurations whose 
  structures do not vary significantly with time, we attempted
  to learn more about their time-averaged structures by studying ensembles of simulations.
%  Disorder among head groups in the simulated atomistic systems is largely determined
%  by each system's quenched configuration. We observe rapid reorganization of our 
%  initial configurations into configurations with quenched disorder that does not
%  vary significantly for the remainder of the
%  simulation time. For that reason, 
  We created ensembles of 40 simulations in both the parallel displaced and 
  sandwiched configurations. We used the same equilibration technique as above 
  (see section~\ref{section:equilibration}), however we built the initial
  configurations with randomly displaced columns in the $z$-direction and
  then stopped their equilibration after 5 ns of unrestrained simulation. We 
  simulated XRD patterns from the 40 concatenated trajectories. The $q_r$ 
  cross-sections of R-$\pi$ generated from the two concatenated trajectories are shown
  in Figure~\ref{fig:ensemble_XRD}. Qualitatively, the cross-sections
  of are nearly smooth, with small spikes near $q_r$=0. The data 
  suggests that the average intensity of R-$\pi$ in sandwiched systems is 
  about 3$\times$ higher than that in the parallel displaced configuration. 
  Overall, the intensity of R-$\pi$ generated from the parallel displaced 
  ensemble shows the best agreement with experiment so far. For simplicity, 
  we will limit the following discussion to the parallel displaced configuration.
  Equivalent data is available for the sandwiched configuration in the
  supporting information. %BJC15: to be added
  %BJC15: limiting discussion to parallel displaced since it seems most consistent with experiment
  % However, I can switch it to sandwiched very easily. The discussion below will remain the same

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_rsection.png}
  \caption{Sandwiched}\label{fig:sandwiched_ensemble_rsection}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_rsection.png}
  \caption{Parallel Displaced}\label{fig:offset_ensemble_rsection}
  \end{subfigure}
  \caption{The $q_r$ section of R-$\pi$ is much smoother when we generate simulated XRD
  		   patterns from an ensemble of 40 independent simulations. The maximum 
  		   intensity of R-$\pi$ is 3$\times$ higher in the sandwiched configuration (a)
  		   than in the parallel displaced configuration (b).}\label{fig:ensemble_XRD}
  \end{figure}

  Independent simulations exhibit similar amounts of quenched disorder. 
  We pooled the deviations of each head group COM from idealized positions
  from all independent simulations in order to create the distributions shown in 
  Figure~\ref{fig:offset_ensemble_pooled} 
  (see section~\ref{method:simple_systems}). The distributions appear 
  symmetric meaning that there is an equal chance for a head group to displace
  in the positive or negative $z$, $r$ or $\theta$-direction. We verified that
  this is the case for individual COMs. 
  % For a given system, there are 400 head groups. 
  If we consider the COM of a given head group, we expect that the
  distribution of its deviations from its idealized position among all the 
  independent simulations
%  the $z$, $r$, and $\theta$ directions 
  should be symmetric about its idealized position. We can calculate the 
  empirical cumulative distribution function (ECDF) 
  of these distributions of deviations. 
  % Each ECDF contains 40 data points, one from each independent simulation.
  The ECDFs of 3 randomly selected COMs
  are shown in Figure~\ref{fig:offset_ecdfs} (colored lines). The average 
  of all COM ECDFs is represented by the red line with the 95 \% confidence
  interval represented by the red error bars. We also calculated 
  the ECDF from the full distributions in Figure~\ref{fig:offset_ensemble_pooled}
  (black line with error bars). We generated error bars that represent the 95\% 
  confidence intervals, by performing 1000 trials where we randomly sampled 40
  values (the same as the number of independent simulations) from the distributions in 
  Figure~\ref{fig:offset_ensemble_pooled}, then measured the deviation between
  the sampled ECDF and the full ECDF. These error bars are generally smaller than
  those generated from the 400 COM ECDFs. This is because there is a wider
  distribution of mean COM deviations than the mean deviations from distributions
  sampled from the full distribution. The above evidence supports that each quenched
  configuration is random and mostly independent.

  %BJC15: will not waste much time formatting until we converge on a figure 
  \begin{figure}[!htb]
  \centering
%  \begin{subfigure}{\textwidth}
%  \includegraphics[width=\textwidth]{sandwiched_ensemble_pooled.png}
%  \caption{Sandwiched}\label{fig:sandwiched_ensemble_pooled.png}
%  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_pooled.png}
  \caption{Distributions of deviations from ideal positions generated with data
  from all independent simulations}\label{fig:offset_ensemble_pooled}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  % BJC15: I don't think it's necessary to put the 3 randomly selected ECDFs in since it
  % doesn't provide extra information and clutters the figure. Left there for now.
  % BJC15: Also, do you have a preference for 1-sigma or 95 % confidence intervals? I think the 95 % is fine as is
  \includegraphics[width=\textwidth]{offset_ecdfs.png}
  \caption{Empirical cumulative distribution functions generated from (a) and
  from simulation ensembles.}\label{fig:offset_ecdfs}
  \end{subfigure}
  \caption{(a) The distributions of the head group COM deviations
  from their idealized positions generated using pooled data from all
  frames of each independent configuration is symmetric. This implies that 
  there is equal probability for a head group to displace in the positive
  or negative $z$, $r$ or $\theta$-direction. (b) The COM position of a 
  given head group is displaced randomly upon quenching. The ECDF generated from
  the pooled distributions (black) in (a) agree with the means of the 
  ECDFs generated from each COM (red). The red error bars are larger than
  the black error bars since there is a wider distribution of mean COM
  deviations than the mean deviations of distributions sampled from the full
  distribution.}\label{fig:full_ensemble_distributions}
  \end{figure}

  % BJC15: How important is it to prove in the main text (rather than supporting)
  % that the long systems sample the same distribution as above. Since they were
  % generated using the same procedure, why should the reader question it?

  The systems that we ran for 400 ns and used for most of our analysis are
  representative of the long term simulation behavior of any system chosen from the 
  ensemble. The distributions of standard deviations generated from each of
  the ensemble trajectories (Figures~\ref{fig:offset_ensemble_stds} 
  and~\ref{fig:offset_ensemble_means}) are fairly tight with ($\sigma_{\sigma_z}$,
  $\sigma_{\sigma_r}$, $\sigma_{\sigma_\theta}$) = (0.011 nm, 0.007 nm , 0.022 radians).
  We analyzed the first 5 ns of the 400 ns ordered parallel displaced
  configuration and observe the same amount of disorder (based on the $\sigma$ values
  in Figure~\ref{fig:offset_ensemble_stds}) with indistinguishable 
  mean values. Additionally, we calculated the radial density of monomer components as a 
  function of their distance from the pore centers (Figure~\ref{fig:offset_ensemble_regional_density}).
  All simulations have similar profiles. The distribution of sodium ions near the
  pore center is relatively noisy since the sodium ions are have much more 
  translational freedom than the head groups.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_stds.png}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_means.png}
  \caption{}\label{fig:offset_ensemble_means}
  % BJC15: The mean z-value seems a little silly since it is basically zero except for numerical error I presume
  % The mean is required to be zero for the calculation to work since columns are randomly displaced.
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.png}
  %BJC15: I can explicitly define the colors for each system since all the ugly colors come out on top
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main ordered parallel displaced system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $z$, $r$ and $\theta$ from the first 5 ns of the main
  system (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
  main system simulation trajectory (black lines) and from the ensemble of 
  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
  \end{figure}

  We can explain the discrepancies between R-$\pi$ seen experimentally
  and in simulation using what we have shown in this section. The stacking
  distance between monomer head groups is too large, likely due to failures
  of the force field to appropriately model $\pi-\pi$ interactions. The intensity
  of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
  ordering in the $z$-direction in addition to high degrees of correlation 
  between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
  which is also likely a consequence of columns that are too highly correlated.
  If we limit ourselves to standard simulation techniques, it is necessary to 
  average data generated from ensembles of independent simulation trajectories
  in order to begin converging on time-averaged descriptions of the system's
  molecular structure.

  % BJC15 : Matt comment: "I found the discussion of pore structure in the first 
  % full paragraph on page 38 is a bit hard to follow. Maybe a schematic of what 
  % “in between sandwiched and parallel displaced” looks like would be helpful"
  % BJC15: could move figure to supplemental to save space
  % BJC15: Added a transition type clause to the beginning of this first sentence
  % to help with flow. It might be too much though.
  A secondary conclusion that we've drawn from the evidence in this section is 
  that the architecture of each column is likely in between our sandwiched
  and parallel displaced configurations. The parallel displaced configuration 
  that we have simulated in this paper is an exaggerated manifestation of the 
  parallel displaced $\pi-\pi$ stacking mode. Not only is the intensity of R-$\pi$
  calculated from the ensemble of parallel displaced simulations in close agreement
  with experiment, but the experimental WAXS pattern shows faint off-axis features
  at the same $q_r$ value as R-double which are only present in simulated patterns
  generated from parallel displaced configurations. The monomers may prefer to be
  parallel displaced, but their displacement is likely only slightly shifted, on 
  the $xy$ plane, from the center of mass of their vertically adjacent neighbors 
  (See Figure~\ref{fig:between_pd}). In this way, columns can more easily act 
  independently while maintaining a parallel displaced structure. It is hard to
  imagine parallel displaced columns, as we have set them up, acting independently 
  unless we force them to be that way, as we did to create the ensemble of parallel
  displaced simulations.

  %BJC15: figure in response to Matt
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{pd_36.eps}
  \caption{}\label{fig:pd_36}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{pd_lt36.eps}
  \caption{}\label{fig:pd_lt36}
  \end{subfigure}
  \caption{Head groups are likely stack in a configuration between sandwiched and
  parallel displaced. (a) In our parallel displaced configurations with 5 monomers 
  per columns, we placed head groups so the angle, $\theta$, between vectors extending
  from vertically stacked head groups to the pore center equals 36$\degree$ 
  ((360$\degree$ / $ncol$) / 2 where $ncol$ is the number of columns per pore). 
  (b) In the true configuration, $\theta$ is likely between 0$\degree$ and 36 $\degree$.
  When $\theta$=0$\degree$, the system architecture is the same as a sandwiched 
  configuration.}\label{fig:between_pd}
  \end{figure}

@@

  % BJC15: first pass at a brief future work paragraph
  Future work, based on what has been learned in this study, may help further improve the 
  structural agreement between experiment and simulation. We may be able to 
  modify the GAFF force field or use a different force field in order to better
  capture the $\pi-\pi$ interactions which draw stacked monomers closer together. 
  We can study ensembles of long simulations in order to observe more averaged 
  structure and to create more experimentally consistent XRD patterns. Finally, we can
  run extremely long simulations (on the order of \SI{}{\micro s}) in order to better 
  quantify the time scales for large scale rearrangements to occur.

  With the structural understanding gained by these simulations, it will becomes
  possible to evaluate transport of various solutes within the system, and apply the
  knowledge gained from this study in order to suggest improvements to the
  existing system as well as to evaluate new unsynthesized LLC systems.

>>>>

  Since the dynamics of this system are slow, and consequently most of
  our analysis has been focused on a set of quenched configurations with some structural characteristics that do not 
  vary significantly with time, we attempted
  to learn more about their time-averaged structures by studying ensembles of shorter simulations started
  from more independent initial configurations.
%  Disorder among head groups in the simulated atomistic systems is largely determined
%  by each system's quenched configuration. We observe rapid reorganization of our 
%  initial configurations into configurations with quenched disorder that does not
%  vary significantly for the remainder of the
%  simulation time. For that reason, 
  We created ensembles of 40 simulations in both the parallel displaced and 
  sandwiched configurations. We used the same equilibration scheme as above 
  (see section~\ref{section:equilibration}). However, we built the initial
  configurations with randomly displaced columns in the $z$-direction and
  looked at the results after 5 ns of unrestrained simulation, which should capture any quenched disorder built in 
  from the initial configurations. We 
  then simulated XRD patterns from the 40 trajectories, concatenated together. The $q_r$ 
  cross-sections of R-$\pi$ generated from the two concatenated trajectories are shown
  in Figure~\ref{fig:ensemble_XRD}. Qualitatively, the cross-sections
  of are nearly smooth, with only small spikes near $q_r$=0. These data 
  %MRS15: for sentence below - qualify about the ensemble?
  suggest that the average intensity of R-$\pi$ in sandwiched systems is 
  about 3$\times$ higher than that in the parallel displaced configuration. 
  %MRS16: probably don't want to talk about which combination BEST agrees with the ensemble,
  %but present the different things that in combination would explain most of the differences.
  Overall, the intensity of R-$\pi$ generated from the parallel displaced 
  ensemble shows the best agreement with experiment so far. For simplicity, 
  we will limit the following discussion to the parallel displaced configuration.
  Equivalent data is available for the sandwiched configuration in the
  supporting information. %BJC15: to be added
  %BJC15: limiting discussion to parallel displaced since it seems most consistent with experiment
  % However, I can switch it to sandwiched very easily. The discussion below will remain the same
  %MRS15: I think better to just talk about how much things can be reduced in height.  If there are OTHER features that look more characteristic of the experiment in parallel displaced, you can talk about those.
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_rsection.png}
  \caption{Sandwiched}\label{fig:sandwiched_ensemble_rsection}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_rsection.png}
  \caption{Parallel Displaced}\label{fig:offset_ensemble_rsection}
  \end{subfigure}
  \caption{The $q_r$ section of R-$\pi$ is much smoother when we generate simulated XRD
  		   patterns from an ensemble of 40 independent simulations, suggesting that much of the extra initial intensity may be due to the starting conditions. The maximum 
  		   intensity of R-$\pi$ is 3$\times$ higher in the sandwiched configuration (a)
  		   than in the parallel displaced configuration (b).}\label{fig:ensemble_XRD}
  \end{figure}

  These short independent simulations exhibit similar amounts of quenched disorder. 
  We pooled the deviations of each head group COM from idealized positions
  from all independent simulations in order to create the distributions shown in 
  Figure~\ref{fig:offset_ensemble_pooled} 
  (see section~\ref{method:simple_systems}). The distributions appear 
  symmetric meaning that there is an equal chance for a head group to displace
  in the positive or negative $z$, $r$ or $\theta$-direction. We verified that
  this is the case for individual COMs. 
  % For a given system, there are 400 head groups. 
  If we consider the COM of a given head group, we expect that the
  distribution of its deviations from its idealized position among all the 
  independent simulations
%  the $z$, $r$, and $\theta$ directions 
  should be symmetric about its idealized position. We can calculate the 
  empirical cumulative distribution function (ECDF) 
  of these distributions of deviations. 
  % Each ECDF contains 40 data points, one from each independent simulation.
  The ECDFs of 3 randomly selected COMs
  are shown in Figure~\ref{fig:offset_ecdfs} to guide the eye (colored lines). The average 
  of all COM ECDFs is represented by the red line with the 95 \% confidence
  interval represented by the red error bars. We also calculated 
  the ECDF from the full distributions in Figure~\ref{fig:offset_ensemble_pooled}
  (black line with error bars). We generated error bars that represent the 95\% 
  confidence intervals, by performing 1000 trials where we randomly sampled 40
  values (the same as the number of independent simulations) from the distributions in 
  Figure~\ref{fig:offset_ensemble_pooled}, then measured the deviation between
  the sampled ECDF and the full ECDF. These error bars are generally smaller than
  those generated from the 400 COM ECDFs, as there is a wider
  distribution of mean COM deviations than the mean deviations from distributions
  sampled from the full distribution. The similarity between entirely indepdently sampled CDFs and the CDFs from individual independent simulations supports the that each quenched configuration is random and mostly independent.

  %BJC15: will not waste much time formatting until we converge on a figure 
  \begin{figure}[!htb]
  \centering
%  \begin{subfigure}{\textwidth}
%  \includegraphics[width=\textwidth]{sandwiched_ensemble_pooled.png}
%  \caption{Sandwiched}\label{fig:sandwiched_ensemble_pooled.png}
%  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_pooled.png}
  \caption{Distributions of deviations from ideal positions generated with data
  from all independent simulations}\label{fig:offset_ensemble_pooled}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  % BJC15: I don't think it's necessary to put the 3 randomly selected ECDFs in since it
  % doesn't provide extra information and clutters the figure. Left there for now.
  % MRS15: kind of nice to guide the eye?
  % BJC15: Also, do you have a preference for 1-sigma or 95 % confidence intervals? I think the 95 % is fine as is
  %MRS15: 95% is fine.
  \includegraphics[width=\textwidth]{offset_ecdfs.png}
  \caption{Empirical cumulative distribution functions generated from (a) and
  from simulation ensembles.}\label{fig:offset_ecdfs}
  \end{subfigure}
  \caption{(a) The distributions of the head group COM deviations
  from their idealized positions generated using pooled data from all
  frames of each independent configuration is symmetric, implying that 
  there is equal probability for a head group to displace in the positive
  or negative $z$, $r$ or $\theta$-direction. (b) The COM position of a 
  given head group is displaced randomly upon quenching. The ECDF generated from
  the pooled distributions (black) in (a) agree with the means of the 
  ECDFs generated from each COM (red). The red error bars are larger than
  the black error bars since there is a wider distribution of mean COM
  deviations than the mean deviations of distributions sampled from the full
  distribution.}\label{fig:full_ensemble_distributions}
  \end{figure}

  % BJC15: How important is it to prove in the main text (rather than supporting)
  % that the long systems sample the same distribution as above. Since they were
  % generated using the same procedure, why should the reader question it? 
  % MRS15: because they could all collapse to the SAME (or similar) quenched disorder, rather than 
  % different, mostly independent ones.

  The systems run for 400 ns and used for most of our analysis are
  representative of the long term simulation behavior of any system chosen from the 
  ensemble. The distributions of standard deviations generated from each of
  the ensemble trajectories (Figures~\ref{fig:offset_ensemble_stds} 
  and~\ref{fig:offset_ensemble_means}) are fairly tight with ($\sigma_{\sigma_z}$,
  $\sigma_{\sigma_r}$, $\sigma_{\sigma_\theta}$) = (0.011 nm, 0.007 nm , 0.022 radians).
  We analyzed the first 5 ns of the 400 ns ordered parallel displaced
  configuration and observe the same amount of disorder (based on the $\sigma$ values
  in Figure~\ref{fig:offset_ensemble_stds}) with indistinguishable 
  mean values. Additionally, we calculated the radial density of monomer components as a 
  function of their distance from the pore centers (Figure~\ref{fig:offset_ensemble_regional_density}).
  All simulations have similar profiles. The distribution of sodium ions near the
  pore center is relatively noisy since the sodium ions are have much more 
  translational freedom than the head groups.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_stds.png}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_means.png}
  \caption{}\label{fig:offset_ensemble_means}
  % BJC15: The mean z-value seems a little silly since it is basically zero except for numerical error I presume
  % The mean is required to be zero for the calculation to work since columns are randomly displaced.
  %MRS15: good point.  Probably can leave that off. 
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.png}
  %BJC15: I can explicitly define the colors for each system since all the ugly colors come out on top
  %MRS15: sounds good.  Maybe a bit narrower lines?
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main ordered parallel displaced system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $z$, $r$ and $\theta$ from the first 5 ns of the main
  system (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
  main system simulation trajectory (black lines) and from the ensemble of 
  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
  \end{figure}

  %MRS15: make it more clear that you are now summing up this section.  Perhaps put
  %subheadings in this section, as I discussed.
  We can explain the discrepancies between R-$\pi$ seen experimentally
  and in simulation using what we have shown in this section. The stacking
  distance between monomer head groups is too large, likely due to failures
  of the force field to appropriately model $\pi-\pi$ interactions. The intensity
  of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
  ordering in the $z$-direction in addition to high degrees of correlation 
  between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
  which is also likely a consequence of columns that are too highly correlated.
  If we limit ourselves to standard simulation techniques, it is necessary to 
  average data generated from ensembles of independent simulation trajectories
  in order to begin converging on time-averaged descriptions of the system's
  molecular structure.

  % BJC15 : Matt comment: "I found the discussion of pore structure in the first 
  % full paragraph on page 38 is a bit hard to follow. Maybe a schematic of what 
  % “in between sandwiched and parallel displaced” looks like would be helpful"
  % BJC15: could move figure to supplemental to save space
  % BJC15: Added a transition type clause to the beginning of this first sentence
  % to help with flow. It might be too much though.
  A secondary conclusion drawn from the evidence in this section is 
  that the architecture of each column is likely in between our sandwiched
  and parallel displaced configurations. The parallel displaced configuration 
  that we have simulated in this paper is an exaggerated manifestation of the 
  parallel displaced $\pi-\pi$ stacking mode. Not only is the intensity of R-$\pi$
  calculated from the ensemble of parallel displaced simulations in close agreement
  with experiment, but the experimental WAXS pattern shows faint off-axis features
  at the same $q_r$ value as R-double which are only present in simulated patterns
  generated from parallel displaced configurations. The monomers may prefer to be
  parallel displaced, but their displacement is likely only slightly shifted, on 
  the $xy$ plane, from the center of mass of their vertically adjacent neighbors 
  (See Figure~\ref{fig:between_pd}). In this way, columns can more easily act 
  independently while maintaining some features of parallel displaced structure. 
  %MRS15: yeah, cut the last bit.

  %BJC15: figure in response to Matt.  
  %MRS15: This seems like something for supporting information.
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{pd_36.eps}
  \caption{}\label{fig:pd_36}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{pd_lt36.eps}
  \caption{}\label{fig:pd_lt36}
  \end{subfigure}
  \caption{Head groups are likely stack in a configuration between sandwiched and
  parallel displaced. (a) In our parallel displaced configurations with 5 monomers 
  per columns, we placed head groups so the angle, $\theta$, between vectors extending
  from vertically stacked head groups to the pore center equals 36$\degree$ 
  ((360$\degree$ / $ncol$) / 2 where $ncol$ is the number of columns per pore). 
  (b) In the true configuration, $\theta$ is likely between 0$\degree$ and 36 $\degree$.
  When $\theta$=0$\degree$, the system architecture is the same as a sandwiched 
  configuration.}\label{fig:between_pd}
  \end{figure}

@@

  % BJC15: first pass at a brief future work paragraph
  %MRS15: tweaked.
  Future work, based on what has been learned in this study, may help further improve the 
  structural agreement between experiment and simulation. 
  %We may be able to 
  %modify the GAFF force field or use
  Force fields explicitly including $\pi-\pi$ interactions may be able to draw stacked monomers closer together. 
  We can study ensembles of long simulations in order to observe more averaged 
  structure and to create more experimentally consistent XRD patterns. Extremely long simulations 
  (on the order of \SI{}{\micro s}) may be necessary to better 
  quantify the time scales for large scale rearrangements, and the precise arrangements themselves.

  With the structural understanding gained by these simulations, it will be
  possible to evaluate transport of various solutes within the system, and apply the
  knowledge gained from this study in order to suggest improvements to the
  existing system, as well as to evaluate new unsynthesized LLC systems.
